---
title: "SBA2- HW1"
author: "Chatzimoschou Angeliki"
date: "2016 M04 25"
output: html_document
---

## Question 1
```{r}
library(AER)
library(COUNT)

data("PhDPublications")
View(PhDPublications)
str(PhDPublications)


Poisson_model <- glm(articles~.,data = PhDPublications, family = "poisson")
summary(Poisson_model)
deviance(Poisson_model)
str(Poisson_model)
```

##Question 2
```{r}
DevOverDF <- function(x){
   (deviance(x)/x$df.residual)
}
```

## Question 3
```{r}
DevOverDF(Poisson_model)
```
Since DevOverDF(Poisson_model)= 1.797988 > 1, we have overdispersion in our model.

## Question 4
```{r}
library(qcc)
qcc.overdispersion.test(PhDPublications$articles,type="poisson")
```

## Question 5
Since p-value=0 < 0.05, we reject Ho: no overdispersion.
In conclusion, there is overdispersion in our model.

## Question 6
```{r}
Quasi_Poisson_model <- glm(articles~.,data = PhDPublications, family = "quasipoisson")
summary(Poisson_model)
summary(Quasi_Poisson_model)
```

## Question 7
Yes for a 95% CI both models suggest the same input features related to response variable.

## Question 8
```{r}
set.seed(666)
x1 <- runif(300, min=0, max=1)

set.seed(999)
x2 <- runif(300, min=0, max=1)

set.seed(1985)
x3 <- runif(300, min=0, max=1)

ysum <- 2*x1 + 5.7*x2 - 7.8*x3

set.seed(1988)
y<-rpois(300, exp(ysum))

my_df <- as.data.frame(cbind(x1,x2,x3,y))

my_Poisson1 <- glm(y~. ,family = 'poisson', data = my_df)
my_Poisson2 <- glm(y ~ x1 + x3 ,family = 'poisson', data = my_df)

DevOverDF(my_Poisson1)
DevOverDF(my_Poisson2)
```
In my_Poisson1 model, overdispersion equals 0.81 < 1, so there is no overdispersion in the model.
In my_Poisson2 model, overdispersion equals 30.39 > 1, so there is overdispersion in the model.

## Question 9
```{r}
library(MASS)
NB_model <- glm.nb(articles~.,data = PhDPublications)
```

## Question 10
```{r}
AIC(Poisson_model)
AIC(NB_model)
```
In general we prefer the model with the lowest AIC value. 
In our case that would be the Neg. Binomial model: AIC_Poisson_model = 3314.113 < AIC_NB_model= 3135.917

## Question 11
```{r}
BIC(Poisson_model)
BIC(NB_model)
```
We reach the same results as in Question 10, since BIC works the same way as AIC.